Stock enhancement undermines community stability

### 2022-02-02 rmd/manuscript.Rmd
edit: manuscript

We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios. These scenarios cover a range of ecological contexts, differing in the intrinsic growth of the enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, environmental stochasticity $\sigma_{\epsilon}$, and relative fitness $f_R$ (see **Materials and Methods**). The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of the total community density $\sum_i^SN_i$: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$). We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer mechanisms that underlie the community-level response.

@@

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the stock enhancement of masu salmon (**Figure 1E**), one of Japan's most valuable freshwater resources [@kitadaLessonsJapanMarine2020], on the long-term stability of stream fish communities in Hokkaido, Japan. In the protected watersheds (**Figure 1C and 1D**), a long-term program exists to monitor stream fish communities along with the official stocking records. Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see **Materials and Methods** for selection criteria). Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential confounding effects of climates and local abiotic factors.

As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive stocking (**Figure 1B**). Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**). This pattern was associated with the reduced long-term average of total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2;** see **Tables S8-S10** for full statistics). In the meantime, the SDs had vague relationships with stock enhancement (**Figure 1B and 2**).

Competition is a likely mechanism, as our theory assumes. Field experiments confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018]. Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003]. Importantly, socioeconomic factors control the number of releases (e.g., budget allocation). As such, given the density-dependent regulation of recipient communities, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.

@@

The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996]. Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity. Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community. While our empirical example is limited to stream fish communities, the destabilizing effect emerged across diverse simulated scenarios, implying that this phenomenon is pervasive across terrestrial and aquatic taxa.

We should prioritize habitat preservation and restoration with a broader scope of biodiversity conservation. Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement. Protected areas and environmental restoration are promising tools to conserve biodiversity, and the smart spatial design is key to achieving successful conservation. For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022]. Socioeconomic factors such as governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018]. These considerable potentials indicate that viable management options for the sustainable future exist before blindly accepting stock enhancement. Without a comprehensive framework that appreciates the ecological integrity of natural communities, the stock enhancement will never be effective but impairs biodiversity.

>>>>

We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios. These scenarios cover a range of ecological contexts, differing in the intrinsic growth of the enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, environmental stochasticity $\sigma_{\epsilon}$, and relative fitness $f_R$ (see **Materials and Methods**). Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to stock enhancement: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$). We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer underlying mechanisms.

@@

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the stock enhancement of masu salmon (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan. In the protected watersheds (**Figure 1C and 1D**), a long-term program exists to monitor stream fish communities along with the official stocking records. Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see **Materials and Methods** for selection criteria). Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential confounding effects of climates and local abiotic factors.

As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive stocking (**Figure 1B**). The effect was striking in its magnitude, almost doubling the CV at the highest level of stocking (**Figure 1B**). Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**). This pattern was associated with the reduced long-term average of the total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2;** see **Tables S8-S10** for full statistics). In the meantime, the SDs had vague relationships with stock enhancement (**Figure 1B and 2**).

Competition is a likely mechanism, as our theory assumes. Field experiments confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018]. Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003]. Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the density-dependent regulation of recipient communities. As such, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.

@@

The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996]. Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity. Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the provisioning and delivery of ecosystem services [@cardinaleBiodiversityLossIts2012]. While our empirical example is limited to stream fish communities, we anticipate that this phenomenon is pervasive across terrestrial and aquatic taxa because the destabilizing effect emerged across diverse simulated scenarios.

We should prioritize habitat preservation and restoration with a broader scope of biodiversity conservation. Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement. Protected areas and environmental restoration are promising tools to conserve biodiversity, and the smart spatial design is key to achieving successful conservation. For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022]. Socioeconomic factors such as governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018]. These considerable potentials indicate that viable management options for the sustainable future exist before blindly accepting stock enhancement. Without a comprehensive framework that appreciates the ecological integrity of natural communities, stock enhancement will never be effective but impairs biodiversity.
